---
title: "Simulation"
output: html_document
---


# ------------------------------------------------------
# Load Packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# devtools::install_github("https://github.com/correadarosaj/Economon")
library(Economon)

library(tidyverse)
library(here)
library(lemon)
library(foreach)
library(doParallel)
library(ggpp)
library(ggimage)
```

# renv Snapshot
```{r, eval = F}
renv::snapshot()
```


# ------------------------------------------------------
# Simulation
## Setup
```{r}
#--------------------------------------------------------------------
# SETUP CONDITIONS
commodities = data.frame(b0          = .00075,
                         deprivation = c("Hi", "Lo", "Hi", "Lo"),
                         b1          = c(-.5, -.075, -.5, -.075),
                         satiation   = c("Hi", "Hi", "Lo", "Lo"),
                         b2          = c(4, 4, 1, 1))
sd_b1 = .1 # controls variability for deprivation parameter
sd_b2 = 1  # controls variability for satiation parameter


#--------------------------------------------------------------------
# FUNCTION FOR MAKING LABELS
make_condition_label = function(df, stacked = T){
  if(stacked){
    new_df = df %>% 
      mutate(condition =
             factor(condition, 
                    levels = c("Lo Dep (B1) Lo Sat (B2)", "Hi Dep (B1) Lo Sat (B2)",
                               "Lo Dep (B1) Hi Sat (B2)", "Hi Dep (B1) Hi Sat (B2)"),
                    ordered = T),
           condition_lab =
             factor(condition, 
                    levels = c("Lo Dep (B1) Lo Sat (B2)", "Hi Dep (B1) Lo Sat (B2)",
                               "Lo Dep (B1) Hi Sat (B2)", "Hi Dep (B1) Hi Sat (B2)"),
                    labels = c("Low Dep\nLow Sat", "High Dep\nLow Sat",
                               "Low Dep\nHigh Sat", "High Dep\nHigh Sat"),
                    ordered = T))
  } else {
    new_df = df %>% 
      mutate(condition =
             factor(condition, 
                    levels = c("Lo Dep (B1) Lo Sat (B2)", "Hi Dep (B1) Lo Sat (B2)",
                               "Lo Dep (B1) Hi Sat (B2)", "Hi Dep (B1) Hi Sat (B2)"),
                    ordered = T),
           condition_lab =
             factor(condition, 
                    levels = c("Lo Dep (B1) Lo Sat (B2)", "Hi Dep (B1) Lo Sat (B2)",
                               "Lo Dep (B1) Hi Sat (B2)", "Hi Dep (B1) Hi Sat (B2)"),
                    labels = c("Low Dep Low Sat", "High Dep Low Sat",
                               "Low Dep High Sat", "High Dep High Sat"),
                    ordered = T))
  }
  return(new_df)
}


#--------------------------------------------------------------------
# SETUP FOR SIMULATION
clusters = makeCluster(4)
burnin = 200
n_trials = 500
n_simulations = 100
```


## Run Simulation
```{r, eval = F}
#--------------------------------------------------------------------
# SIMULATION
set.seed(20240604)
registerDoParallel(clusters)
full_population = 
  foreach(commodity = 1:nrow(commodities), .combine = "rbind") %dopar% {
    require(tidyverse)
    require(Economon)
    require(foreach)
    foreach(i = 1:n_simulations, .combine = "rbind") %do% {
      cur_parameters =
        data.frame(alpha_b0 = exp(rnorm(1, mean = log(commodities$b0[commodity]), sd = 0)),
                   alpha_b1 = rnorm(1, mean = commodities$b1[commodity], sd = sd_b1),
                   alpha_b2 = rnorm(1, mean = commodities$b2[commodity], sd = sd_b2)) %>% 
        mutate(alpha_b1 = case_when(alpha_b1 >= 0 | alpha_b1 <= -1 ~ commodities$b1[commodity], T ~ alpha_b1),
               alpha_b2 = case_when(alpha_b2 <= 0 ~ commodities$b2[commodity], T ~ alpha_b2))
      
      
      generate_market(
        n_trials = n_trials+burnin,
        condition = paste(commodities$deprivation[commodity], "Dep (B1)",
                          commodities$satiation[commodity], "Sat (B2)"),
        alpha_b0 = cur_parameters$alpha_b0, alpha_s0 = .005,
        alpha_b1 = cur_parameters$alpha_b1,
        alpha_b2 = cur_parameters$alpha_b2) %>% 
        mutate(simulation = i)
    }
  }
stopCluster(clusters)


#--------------------------------------------------------------------
# SAVE SIMULATION
saveRDS(full_population, here("Data",  "Full_Population.RDS"))
```


```{r}
full_population = readRDS(here("Data",  "Full_Population.RDS"))
```


## Check Parameters
```{r, eval = F}
full_population %>% 
  group_by(condition, simulation) %>% 
  reframe(alpha_b1 = mean(alpha_b1),
          alpha_b2 = mean(alpha_b2)) %>%
  pivot_longer(c("alpha_b1", "alpha_b2"), names_to = "alpha_type", values_to = "Alpha Value") %>% 
  mutate(alpha_type = case_when(alpha_type == "alpha_b1" ~ "Alpha B1", T ~ "Alpha B2")) %>% 
  select(Condition = condition, Simulation = simulation, everything()) %>% 
  ggplot(aes(x = Simulation, y = `Alpha Value`, color = Condition)) +
    geom_line() +
    theme_classic() +
    facet_rep_grid(alpha_type~., scales = "free")
```


## Subset Participants
```{r}
population = full_population %>% 
  mutate(trial = trial - burnin,
         transaction = case_when(transaction == 1 ~ "Successful Transaction",
                                 T ~ "Failed Transaction")) %>%
  filter(trial <= 200) %>%  # remove extra samples
  filter(trial > 0)         # remove burn-in

individuals = commodities %>% 
  mutate(condition = paste(deprivation, "Dep (B1)",
                           satiation, "Sat (B2)")) %>% 
  left_join(population) %>%
  mutate(b1_diff = b1-alpha_b1,
         b2_diff = b2-alpha_b2) %>% 
  group_by(condition) %>% 
  mutate(z_b1_diff = (mean(b1_diff) - b1_diff) / sd(b1_diff),
         z_b2_diff = (mean(b2_diff) - b2_diff) / sd(b2_diff),
         error = abs(z_b1_diff) + abs(z_b2_diff),
         min_error = min(error)) %>%
  filter(error == min_error) %>% 
  select(-c(b1_diff, b2_diff, z_b1_diff, z_b2_diff, error, min_error))
```


# ------------------------------------------------------
# Figure 3: Sequential Demand Curves (w/o Seller)
## Make Demand Data
```{r}
sequence_data = individuals %>% 
  filter(condition == "Hi Dep (B1) Hi Sat (B2)" & trial %in% 1:6 |
         condition == "Hi Dep (B1) Lo Sat (B2)" & trial %in% 1:6 |
         condition == "Lo Dep (B1) Hi Sat (B2)" & trial %in% 19:24 |
         condition == "Lo Dep (B1) Lo Sat (B2)" & trial %in% 1:6) %>%
  group_by(condition) %>% 
  mutate(new_trial = rank(trial))

price_ranges = c(.01, 1000)
sequential_demand = data.frame()
previous_demand = data.frame()

for(i in 1:6){
  for(cur_condition in unique(individuals$condition)){
    cur_alpha_B = 
      filter(sequence_data, new_trial == i & condition == cur_condition)$buyer_alpha
    cur.transaction = 
      str_remove(filter(sequence_data, new_trial == i & condition == cur_condition)$transaction, " Transaction")
    
    current_demand =
      data.frame(trial = i, alpha_B = cur_alpha_B,
                 price = 10^(seq(log10(price_ranges[1]), log10(price_ranges[2]), length.out = 100)),
                 condition = cur_condition, transaction = cur.transaction) %>% 
      mutate(Q = calculate_QB(price, alpha_B = alpha_B),
             logQ = log10(Q), log_price = log10(price),
             alpha_B = format(cur_alpha_B, scientific = T, digits = 2))
    previous_demand = bind_rows(mutate(current_demand, trial = i-1),
                                previous_demand) %>% 
      filter(trial > 0)
    sequential_demand = bind_rows(sequential_demand,
                                  current_demand) %>% 
      filter(trial <= 5)
  }
}
```


## Letters for Transaction Success/Fail
```{r}
jpeg(here("Plots", "Figure 3 (Letters) - Person-Level Sequential Demand Curves.jpeg"),
       width = 14.6, height = 11, units = "cm", res = 300)
  sequential_demand %>% 
    make_condition_label() %>% 
    mutate(condition_lab = case_when(trial == 5 ~ condition_lab),
           transaction = case_when(transaction == "Successful" ~ "S", T ~ "F")) %>% 
    ggplot(aes(x = log_price, color = condition)) +
      # GEOMS
      geom_text_npc(aes(npcx = "left", npcy = "bottom", label = transaction)) +
      geom_text_npc(aes(npcx = "right", npcy = "top", label = condition_lab), size = 2.5, hjust = 1) +
      geom_line(aes(y = Q)) +
      geom_line(data = make_condition_label(previous_demand), aes(y = Q), linetype = "dashed") +
      geom_vline(xintercept = log10(calculate_price(.0025)), linetype = "dotted") +
      # SCALES
      scale_x_continuous(expand = c(0, 0), limits = c(log10(price_ranges[1]), log10(price_ranges[2])),
                         breaks = log10(c(.10, 5, 250)),
                         labels = c("$.10", "$5", "$250")) +
      scale_y_continuous(limits = c(0,100), expand = expansion(add = c(0, 2.5)),
                         breaks = c(0, 50, 100),
                         labels = c("0%", "50%", "100%")) +
      scale_linetype_manual(values = c("solid", "dashed")) +
      scale_color_manual(values = c("purple2", "goldenrod3", "green3", "dodgerblue3")) +
      # THEMES
      labs(x = "Price/Commodity", y = "P(Buy)") +
      theme_classic() +
      theme(legend.position = "none",
            strip.background = element_rect(fill = "transparent", colour = "transparent"),
            strip.text.y = element_blank(),
            axis.text = element_text(size = 9, color = "black"),
            axis.title = element_text(size = 12),
            panel.spacing.x = unit(.15, "cm"),
            panel.spacing.y = unit(.3, "cm"),
            plot.margin = unit(c(.15, .2, .075, .3), "cm")) +
      facet_rep_grid(condition~trial,
                     labeller = labeller(trial = c("1" = "Trial 1", "2" = "Trial 2",
                                                   "3" = "Trial 3", "4" = "Trial 4",
                                                   "5" = "Trial 5", "6" = "Trial 6")))
dev.off()
```


## Symbols for Transaction Success/Fail
```{r}
jpeg(here("Plots", "Figure 3 (Symbols) - Person-Level Sequential Demand Curves.jpeg"),
       width = 14.6, height = 11, units = "cm", res = 300)
  sequential_demand %>% 
    make_condition_label() %>% 
    mutate(condition_lab = case_when(trial == 5 ~ condition_lab),
           transaction_image = case_when(transaction == "Successful" ~
                                           here("Plots", "Successful Transaction Symbol.tif"),
                                         transaction == "Failed" ~
                                           here("Plots", "Failed Transaction Symbol.tif"))) %>% 
    ggplot(aes(x = log_price, color = condition)) +
      # GEOMS
      geom_image(aes(x = log10(.0375), y = 12.5, image = transaction_image), size = .2,
                 inherit.aes = F) +
      geom_text_npc(aes(npcx = "right", npcy = "top", label = condition_lab),
                    check_overlap = T, size = 2.5, hjust = 1) +
      geom_line(aes(y = Q)) +
      geom_line(data = make_condition_label(previous_demand), aes(y = Q), linetype = "dashed") +
      geom_vline(xintercept = log10(calculate_price(.0025)), linetype = "dotted") +
      # SCALES
      scale_x_continuous(expand = c(0, 0), limits = c(log10(price_ranges[1]), log10(price_ranges[2])),
                         breaks = log10(c(.10, 5, 250)),
                         labels = c("$.10", "$5", "$250")) +
      scale_y_continuous(limits = c(0,100), expand = expansion(add = c(0, 2.5)),
                         breaks = c(0, 50, 100),
                         labels = c("0%", "50%", "100%")) +
      scale_linetype_manual(values = c("solid", "dashed")) +
      scale_color_manual(values = c("purple2", "goldenrod3", "green3", "dodgerblue3")) +
      # THEMES
      labs(x = "Price/Commodity", y = "P(Buy)") +
      theme_classic() +
      theme(legend.position = "none",
            strip.background = element_rect(fill = "transparent", colour = "transparent"),
            strip.text.y = element_blank(),
            axis.text = element_text(size = 9, color = "black"),
            axis.title = element_text(size = 12),
            panel.spacing.x = unit(.15, "cm"),
            panel.spacing.y = unit(.3, "cm"),
            plot.margin = unit(c(.15, .2, .075, .3), "cm")) +
      facet_rep_grid(condition~trial,
                     labeller = labeller(trial = c("1" = "Trial 1", "2" = "Trial 2",
                                                   "3" = "Trial 3", "4" = "Trial 4",
                                                   "5" = "Trial 5", "6" = "Trial 6")))
dev.off()
```


# ------------------------------------------------------
# Figure 4: Person-Level Purchase Probabilities
## Color 1st Trials
```{r, eval = T}
subsetted_individuals = individuals %>% 
  filter(trial <= 6) %>% 
  make_condition_label()

jpeg(here("Plots", "Figure 4 (Color 1st Trials) - Person-Level Purchase Probabilities.jpeg"),
       width = 7, height = 13, units = "cm", res = 300)
  individuals %>% 
    make_condition_label() %>%
    ggplot(aes(x = trial, y = prob.buy, color = condition_lab)) +
      # geoms
      geom_line(color = "black") +
      geom_point(aes(shape = transaction, size = transaction), fill = "white", color = "black") +
      geom_line(data = make_condition_label(subsetted_individuals)) +
      geom_point(data = make_condition_label(subsetted_individuals),
                 aes(shape = transaction, size = transaction), fill = "white") +
      # scales
      scale_shape_manual(values = c(21, 16)) +
      scale_size_manual(values = c(1, 1.25)) +
      scale_x_continuous(limits = c(0,200),
                         expand = expansion(add = c(1.5, 1.5)), n.breaks = 5) +
      scale_y_continuous(limits = c(0,1), expand = expansion(add = c(0, .025)),
                         breaks = c(0, .5, 1),
                         labels = c("0%", "50%", "100%")) +
      scale_color_manual(values = c("purple2", "goldenrod3", "green3", "dodgerblue3")) +
      # themes
      labs(x = "Transaction", y = "P(Buy)") +
      coord_cartesian(clip = "off") +
      theme_classic() +
      theme(legend.position = "none",
            plot.margin = unit(c(.25, .3, .1, .3), "cm"),
            panel.spacing = unit(.25, "cm"),
            axis.text = element_text(color = "black"),
            strip.text = element_text(hjust = 0),
            strip.background = element_rect(fill = "transparent", colour = "transparent"),
            panel.background = element_rect(fill = "transparent", colour = "transparent"),
            plot.background = element_rect(fill = "transparent", color = "transparent")) +
      guides(color = F, size = F, shape = guide_legend(override.aes = list(size =  2, stroke = .5))) +
      facet_rep_wrap(condition_lab~., nrow = 4)
dev.off()
```


## Black 1st Trials
```{r, eval = T}
subsetted_individuals = individuals %>% 
  filter(trial <= 6) %>% 
  make_condition_label()

jpeg(here("Plots", "Figure 4 (Black 1st Trials) - Person-Level Purchase Probabilities.jpeg"),
       width = 7, height = 13, units = "cm", res = 300)
  individuals %>% 
    make_condition_label() %>%
    ggplot(aes(x = trial, y = prob.buy, color = condition_lab)) +
      # geoms
      geom_line() +
      geom_point(aes(shape = transaction, size = transaction), fill = "white") +
      geom_line(data = make_condition_label(subsetted_individuals), color = "black") +
      geom_point(data = make_condition_label(subsetted_individuals),
                 aes(shape = transaction, size = transaction),
                 fill = "white", color = "black") +
      # scales
      scale_shape_manual(values = c(21, 16)) +
      scale_size_manual(values = c(1, 1.25)) +
      scale_x_continuous(limits = c(0,200),
                         expand = expansion(add = c(1.5, 1.5)), n.breaks = 5) +
      scale_y_continuous(limits = c(0,1), expand = expansion(add = c(0, .025)),
                         breaks = c(0, .5, 1),
                         labels = c("0%", "50%", "100%")) +
      scale_color_manual(values = c("purple2", "goldenrod3", "green3", "dodgerblue3")) +
      # themes
      labs(x = "Transaction", y = "P(Buy)") +
      coord_cartesian(clip = "off") +
      theme_classic() +
      theme(legend.position = "none",
            plot.margin = unit(c(.25, .3, .1, .3), "cm"),
            panel.spacing = unit(.25, "cm"),
            axis.text = element_text(color = "black"),
            strip.text = element_text(hjust = 0),
            strip.background = element_rect(fill = "transparent", colour = "transparent"),
            panel.background = element_rect(fill = "transparent", colour = "transparent"),
            plot.background = element_rect(fill = "transparent", color = "transparent")) +
      guides(color = F, size = F, shape = guide_legend(override.aes = list(size =  2, stroke = .5))) +
      facet_rep_wrap(condition_lab~., nrow = 4)
dev.off()
```


## Full Color
```{r, eval = T}
subsetted_individuals = individuals %>% 
  filter(trial <= 6) %>% 
  make_condition_label()

jpeg(here("Plots", "Figure 4 (Full Color) - Person-Level Purchase Probabilities.jpeg"),
       width = 7, height = 13, units = "cm", res = 300)
  individuals %>% 
    make_condition_label() %>%
    ggplot(aes(x = trial, y = prob.buy, color = condition_lab)) +
      # geoms
      geom_line(alpha = .5) +
      geom_point(aes(shape = transaction, size = transaction), fill = "white", alpha = .5) +
      geom_line(data = make_condition_label(subsetted_individuals)) +
      geom_point(data = make_condition_label(subsetted_individuals),
                 aes(shape = transaction, size = transaction), fill = "white") +
      # scales
      scale_shape_manual(values = c(21, 16)) +
      scale_size_manual(values = c(1, 1.25)) +
      scale_x_continuous(limits = c(0,200),
                         expand = expansion(add = c(1.5, 1.5)), n.breaks = 5) +
      scale_y_continuous(limits = c(0,1), expand = expansion(add = c(0, .025)),
                         breaks = c(0, .5, 1),
                         labels = c("0%", "50%", "100%")) +
      scale_color_manual(values = c("purple2", "goldenrod3", "green3", "dodgerblue3")) +
      # themes
      labs(x = "Transaction", y = "P(Buy)") +
      coord_cartesian(clip = "off") +
      theme_classic() +
      theme(legend.position = "none",
            plot.margin = unit(c(.25, .3, .1, .3), "cm"),
            panel.spacing = unit(.25, "cm"),
            axis.text = element_text(color = "black"),
            strip.text = element_text(hjust = 0),
            strip.background = element_rect(fill = "transparent", colour = "transparent"),
            panel.background = element_rect(fill = "transparent", colour = "transparent"),
            plot.background = element_rect(fill = "transparent", color = "transparent")) +
      guides(color = F, size = F, shape = guide_legend(override.aes = list(size =  2, stroke = .5))) +
      facet_rep_wrap(condition_lab~., nrow = 4)
dev.off()
```


# ------------------------------------------------------
# Figure 5: Population-Level Purchase Probabilities
## No Aggregating
```{r, eval = T}
jpeg(here("Plots", "Figure 5 (No Aggregating) - Population-Level Purchase Probabilities.jpeg"),
       width = 7, height = 13, units = "cm", res = 300)
  population %>% 
    make_condition_label(stacked = F) %>%
    ggplot(aes(x = trial, y = prob.buy, color = condition_lab, fill = condition_lab)) +
      # geoms
      geom_line(alpha = .5) +
      geom_line(data = make_condition_label(individuals, stacked = F)) +
      geom_point(data = make_condition_label(individuals, stacked = F),
                 aes(shape = transaction, size = transaction), fill = "white") +
      # scales
      scale_shape_manual(values = c(21, 16)) +
      scale_size_manual(values = c(1, 1.25)) +
      scale_x_continuous(limits = c(0,200),
                         expand = expansion(add = c(1.5, 1.5)), n.breaks = 5) +
      scale_y_continuous(limits = c(0,1), expand = expansion(add = c(0, .025)),
                         breaks = c(0, .5, 1),
                         labels = c("0%", "50%", "100%")) +
      scale_color_manual(values = c("purple2", "goldenrod3", "green3", "dodgerblue3")) +
      scale_fill_manual(values = c("purple2", "goldenrod3", "green3", "dodgerblue3")) +
      # themes
      labs(x = "Transaction", y = "P(Buy)") +
      coord_cartesian(clip = "off") +
      theme_classic() +
      theme(legend.position = "none",
            plot.margin = unit(c(.25, .3, .1, .3), "cm"),
            panel.spacing = unit(.25, "cm"),
            axis.text = element_text(color = "black"),
            strip.text = element_text(hjust = 0),
            strip.background = element_rect(fill = "transparent", colour = "transparent"),
            panel.background = element_rect(fill = "transparent", colour = "transparent"),
            plot.background = element_rect(fill = "transparent", color = "transparent")) +
      guides(color = F, size = F, shape = guide_legend(override.aes = list(size =  2, stroke = .5))) +
      facet_rep_wrap(condition_lab~., nrow = 4)
dev.off()
```


## Ind Faded
```{r, eval = T}
jpeg(here("Plots", "Figure 5 (Lines) - Population-Level Purchase Probabilities.jpeg"),
       width = 7, height = 13, units = "cm", res = 300)
  population %>% 
    group_by(trial, condition) %>% 
    reframe(sd.prob.buy = sd(prob.buy), prob.buy = mean(prob.buy),
            lower = prob.buy - sd.prob.buy, upper = prob.buy + sd.prob.buy,
            lower = case_when(lower < 0 ~ 0, T ~ lower), upper = case_when(upper > 1 ~ 1, T ~ upper)) %>%
    make_condition_label(stacked = F) %>%
    ggplot(aes(x = trial, y = prob.buy, color = condition_lab, fill = condition_lab)) +
      # geoms
      geom_ribbon(aes(ymin = lower, ymax = upper),
                  alpha = .25, color = "transparent") +
      geom_line(linewidth = 1, alpha = .5) +
      geom_line(data = make_condition_label(individuals, stacked = F)) +
      geom_point(data = make_condition_label(individuals, stacked = F),
                 aes(shape = transaction, size = transaction), fill = "white") +
      # scales
      scale_shape_manual(values = c(21, 16)) +
      scale_size_manual(values = c(1, 1.25)) +
      scale_x_continuous(limits = c(0,200),
                         expand = expansion(add = c(1.5, 1.5)), n.breaks = 5) +
      scale_y_continuous(limits = c(0,1), expand = expansion(add = c(0, .025)),
                         breaks = c(0, .5, 1),
                         labels = c("0%", "50%", "100%")) +
      scale_color_manual(values = c("purple2", "goldenrod3", "green3", "dodgerblue3")) +
      scale_fill_manual(values = c("purple2", "goldenrod3", "green3", "dodgerblue3")) +
      # themes
      labs(x = "Transaction", y = "P(Buy)") +
      coord_cartesian(clip = "off") +
      theme_classic() +
      theme(legend.position = "none",
            plot.margin = unit(c(.25, .3, .1, .3), "cm"),
            panel.spacing = unit(.25, "cm"),
            axis.text = element_text(color = "black"),
            strip.text = element_text(hjust = 0),
            strip.background = element_rect(fill = "transparent", colour = "transparent"),
            panel.background = element_rect(fill = "transparent", colour = "transparent"),
            plot.background = element_rect(fill = "transparent", color = "transparent")) +
      guides(color = F, size = F, shape = guide_legend(override.aes = list(size =  2, stroke = .5))) +
      facet_rep_wrap(condition_lab~., nrow = 4)
dev.off()
```


## Quantiles
```{r, eval = T}
jpeg(here("Plots", "Figure 5 (Quantiles) - Population-Level Purchase Probabilities.jpeg"),
       width = 7, height = 13, units = "cm", res = 300)
  population %>% 
    group_by(trial, condition) %>% 
    reframe(lower37.5 = quantile(prob.buy, .125), upper37.5 = quantile(prob.buy, .875),
            lower25 = quantile(prob.buy, .25), upper25 = quantile(prob.buy, .75),
            lower12.5 = quantile(prob.buy, .375), upper12.5 = quantile(prob.buy, .625),
            prob.buy = median(prob.buy)) %>%
    make_condition_label(stacked = F) %>%
    ggplot(aes(x = trial, y = prob.buy, color = condition_lab, fill = condition_lab)) +
      # geoms
      geom_ribbon(aes(ymin = lower37.5, ymax = upper37.5),
                  alpha = .2, color = "transparent") +
      geom_ribbon(aes(ymin = lower25, ymax = upper25),
                  alpha = .3, color = "transparent") +
      geom_ribbon(aes(ymin = lower12.5, ymax = upper12.5),
                  alpha = .4, color = "transparent") +
      geom_line(linewidth = .75, alpha = .5) +
      geom_line(data = make_condition_label(individuals, stacked = F)) +
      geom_point(data = make_condition_label(individuals, stacked = F),
                 aes(shape = transaction, size = transaction), fill = "white") +
      # scales
      scale_shape_manual(values = c(21, 16)) +
      scale_size_manual(values = c(1, 1.25)) +
      scale_x_continuous(limits = c(0,200),
                         expand = expansion(add = c(1.5, 1.5)), n.breaks = 5) +
      scale_y_continuous(limits = c(0,1), expand = expansion(add = c(0, .025)),
                         breaks = c(0, .5, 1),
                         labels = c("0%", "50%", "100%")) +
      scale_color_manual(values = c("purple2", "goldenrod3", "green3", "dodgerblue3")) +
      scale_fill_manual(values = c("purple2", "goldenrod3", "green3", "dodgerblue3")) +
      # themes
      labs(x = "Transaction", y = "P(Buy)") +
      coord_cartesian(clip = "off") +
      theme_classic() +
      theme(legend.position = "none",
            plot.margin = unit(c(.25, .3, .1, .3), "cm"),
            panel.spacing = unit(.25, "cm"),
            axis.text = element_text(color = "black"),
            strip.text = element_text(hjust = 0),
            strip.background = element_rect(fill = "transparent", colour = "transparent"),
            panel.background = element_rect(fill = "transparent", colour = "transparent"),
            plot.background = element_rect(fill = "transparent", color = "transparent")) +
      guides(color = F, size = F, shape = guide_legend(override.aes = list(size =  2, stroke = .5))) +
      facet_rep_wrap(condition_lab~., nrow = 4)
dev.off()
```


## Ind Dots + Pop Lines
```{r, eval = T}
jpeg(here("Plots", "Figure 5 (Ind Dots + Pop Lines) - Population-Level Purchase Probabilities.jpeg"),
       width = 7, height = 13, units = "cm", res = 300)
  population %>% 
    group_by(trial, condition) %>% 
    reframe(sd.prob.buy = sd(prob.buy), prob.buy = mean(prob.buy),
            lower = prob.buy - sd.prob.buy, upper = prob.buy + sd.prob.buy,
            lower = case_when(lower < 0 ~ 0, T ~ lower), upper = case_when(upper > 1 ~ 1, T ~ upper)) %>%
    make_condition_label(stacked = F) %>%
    ggplot(aes(x = trial, y = prob.buy, color = condition_lab, fill = condition_lab)) +
      # geoms
      geom_ribbon(aes(ymin = lower, ymax = upper),
                  alpha = .25, color = "transparent") +
      geom_line() +
      geom_point(data = make_condition_label(individuals, stacked = F),
                 aes(shape = transaction, size = transaction), fill = "white") +
      # scales
      scale_shape_manual(values = c(21, 16)) +
      scale_size_manual(values = c(1, 1.25)) +
      scale_x_continuous(limits = c(0,200),
                         expand = expansion(add = c(1.5, 1.5)), n.breaks = 5) +
      scale_y_continuous(limits = c(0,1), expand = expansion(add = c(0, .025)),
                         breaks = c(0, .5, 1),
                         labels = c("0%", "50%", "100%")) +
      scale_color_manual(values = c("purple2", "goldenrod3", "green3", "dodgerblue3")) +
      scale_fill_manual(values = c("purple2", "goldenrod3", "green3", "dodgerblue3")) +
      # themes
      labs(x = "Transaction", y = "P(Buy)") +
      coord_cartesian(clip = "off") +
      theme_classic() +
      theme(legend.position = "none",
            plot.margin = unit(c(.25, .3, .1, .3), "cm"),
            panel.spacing = unit(.25, "cm"),
            axis.text = element_text(color = "black"),
            strip.text = element_text(hjust = 0),
            strip.background = element_rect(fill = "transparent", colour = "transparent"),
            panel.background = element_rect(fill = "transparent", colour = "transparent"),
            plot.background = element_rect(fill = "transparent", color = "transparent")) +
      guides(color = F, size = F, shape = guide_legend(override.aes = list(size =  2, stroke = .5))) +
      facet_rep_wrap(condition_lab~., nrow = 4)
dev.off()
```


# ------------------------------------------------------
```{r}

```

